Source Summaries

### 2020-04-19 paper/sourceSummaries/summary9.tex
summary 9 initial commit

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{P}ractical {B}luetooth {T}raffic {S}niffing: {S}ystems and {P}rivacy {I}mplications}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{albazrqaoe2016practical}

@@

\noindent
The authors discuss privacy concerns that exist with the prevalence of bluetooth sniffing in todays iot landscape. During their discussion they propose a device of their own creation that can sniff bluetooth traffic effectively using commercially available bluetooth-compliant radios.

@@

\noindent
Game theory is used in this paper as a method of measuring success of the new reader design; Where a win is represented by the readers ability to sniff blbluetooth traffic.

@@

\noindent
The authors improve upon the design of the Ubertooth reciever by modifying the source code to add support for adaptive hop selection and run-time clock synchronization. They also found that the firmware implementation of real-time frequency hopping needed updating to achieve the results they were aiming for.

@@

\noindent
The authors found that their ubertooth implementation is significantly more efficiant than any previous implementation, but does not accommadate for low energy traffic. Therefore their algorithm would need to be modified in order to sniff Bluetooth Low Energy traffic as effectively as they were able to sniff normal bluetooth traffic.

@@

\noindent
The authors point out that their bluetooth sniffer implementation is not configured for BLE traffic. They outline in their paper that some modifications would need to be made to their source code in order for this functionality to be added.
